Buildtime Trend : What's trending in your build process

### 2015-03-31 buildtimetrend/presentation.tex
add project structure diagram
set graphics path
add service link, change link layout

%% Enable license helpers
\graphicspath{{../cc_beamer/}}
\input{../cc_beamer/cc_beamer}

@@

  \includegraphics[scale=.1]{pictures/logo_buildtimetrend.png}

@@

    \includegraphics[scale=.45]{pictures/example_matplotlib_trend.png}

@@

    \includegraphics[scale=.20]{pictures/keenio_workflow.png}\\

@@

    \includegraphics[scale=.45]{pictures/example_dashboard.png}

@@

    Create organisation on GitHub to host the different repositories :
      \item service
      \item client
      \item library (with common functionality)
    <Add project schema>

@@

  \begin{frame}
    \frametitle{Lessons learned}
    \begin{itemize}
      \item start simple
      \item (re)use as much existing tools as possible
      \item start with what you know, learn new skills as you progress
      \item try, even if it is all scary at first
    \end{itemize}
  \end{frame}
  \begin{frame}
   \frametitle{Questions}
    Thanks for your attention!\\
    Questions?
    \vfill
    Dieter Adriaenssens - \href{https://twitter.com/dcadriaenssens}{@dcadriaenssens}
    \vfill
    Buildtime Trend
    \begin{itemize}
      \item Website : \href{https://buildtimetrend.github.io/}{https://buildtimetrend.github.io/}
      \item Twitter : \href{https://twitter.com/buildtime_trend}{@buildtime\_trend}
    \end{itemize}
  \end{frame}
\end{document}

>>>>

%% Enable license helpers
\graphicspath{ {../cc_beamer/}{pictures/} }
\input{../cc_beamer/cc_beamer}

@@

  \includegraphics[scale=.1]{logo_buildtimetrend.png}

@@

    \includegraphics[scale=.45]{example_matplotlib_trend.png}

@@

    \includegraphics[scale=.20]{keenio_workflow.png}\\

@@

    \includegraphics[scale=.45]{example_dashboard.png}

@@

    Create organisation on GitHub to host the different repositories :\\
    \includegraphics[scale=.5]{buildtimetrend_diagram.png}

@@

  \begin{frame}
    \frametitle{Lessons learned}
    \begin{itemize}
      \item start simple
      \item (re)use as much existing tools as possible
      \item start with what you know, learn new skills as you progress
      \item try, even if it is all scary at first
    \end{itemize}
  \end{frame}
  \begin{frame}
   \frametitle{Questions}
    Thanks for your attention!\\
    Questions?
    \vfill
    Dieter Adriaenssens - \href{https://twitter.com/dcadriaenssens}{\small{@dcadriaenssens}}
    \vfill
    Buildtime Trend
    \begin{itemize}
      \item Website : \href{https://buildtimetrend.github.io/}{\small{https://buildtimetrend.github.io/}}
      \item Service : \href{https://buildtimetrend.herokuapp.com/}{\small{https://buildtimetrend.herokuapp.com/}}
      \item Twitter : \href{https://twitter.com/buildtime_trend}{\small{@buildtime\_trend}}
    \end{itemize}
  \end{frame}
\end{document}
